ms_tables_portrait

### 2018-03-26 man/ms_tables_portrait.Rmd
add temperature and prec data

t1raw <- t1raw %>% mutate(name = case_when(
  site == 'caH' ~ 'Cáñar-High', 
  site == 'caL' ~ 'Cáñar-Low',
  site == 'sj' ~ 'San Juan'))

t1 <- t1raw %>% dplyr::select(
  site, lat_m, long_m, elev_mean, slope_mean, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(2,3,5,18,19), round, 2) %>% 
  mutate_at(4, round, 0) %>% 
  mutate_at(c(8:17, 20:21), round, 1) %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  mutate(
    dn = paste0(dn, pare),
    h = paste0(h, pare), 
    age = paste0(age, pare),
    dn_all = paste0(dn_all, pare),
    h_all = paste0(h_all, pare),
    ba = paste0(ba, pare),
    stand_density = paste0(stand_density, pare)) %>% 
  dplyr::select(-pare)

colnames (t1) <- c("Name", "Lat (&deg;)", "Long (&deg;)", "Elevation (m)", "Slope (&deg;)", 
                   "# trees", '# cores', "Dbh (cm)", "Height (m)", "Age (years)", 
                   "Dbh all (cm)", "Height all (m)", "BA (m2/ha)", "Density (trees/ha)")

>>>>

t1raw <- t1raw %>% mutate(name = case_when(
  site == 'caH' ~ 'CA-High', 
  site == 'caL' ~ 'CA-Low',
  site == 'sj' ~ 'SJ'))

t1 <- t1raw %>% dplyr::select(
  name, lat_m, long_m, elev_mean, slope_mean, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(2,3,5,18,19), round, 2) %>% 
  mutate_at(4, round, 0) %>% 
  mutate_at(c(8:17, 20:21), round, 1) %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  mutate(
    dn = paste0(dn, pare),
    h = paste0(h, pare), 
    age = paste0(age, pare),
    dn_all = paste0(dn_all, pare),
    h_all = paste0(h_all, pare),
    ba = paste0(ba, pare),
    stand_density = paste0(stand_density, pare)) %>% 
  dplyr::select(-pare)

# ADD data climate
# clima obsnev (from repo clima SN; son datos de mapas pasados 100 x 100 1960 - 2010)

clima <- read.csv(here("/data/climate_obsnev", "obsnev_qp_pop.csv"), header = TRUE)
cli <- clima %>% filter(pop %in% c(2,6)) %>% mutate_if(is.numeric, funs(round(., 1))) %>% 
  dplyr::select(pop, mean, variable) %>% 
  spread(variable, mean) %>% 
  mutate(name = case_when(
    pop == 2 ~ 'SJ',
    pop == 6 ~ 'CA-High'
  )) %>% dplyr::select(-pop)

# duplicate row for CA site
x <- cli[2,] 
x$name <- 'CA-Low'
cli <- cli %>% bind_rows(x) %>% 
  mutate_at(1, round, 0) %>% 
  unite(temp, c(tmin, tmax), sep=" - ")

t1 <- t1 %>% inner_join(cli, by='name') %>% dplyr::select(name, lat_m, long_m, elev_mean, slope_mean, prec, temp, n_trees:stand_density)

colnames (t1) <- c("Name", "Lat (&deg;)", "Long (&deg;)", "Elevation (m)", "Slope (&deg;)", 
                   "Prec. (mm)", "Temp ((&deg; C)", 
                   "# trees", '# cores', "Dbh (cm)", "Height (m)", "Age (years)", 
                   "Dbh all (cm)", "Height all (m)", "BA (m2/ha)", "Density (trees/ha)")
